R Notebook

### 2021-08-17 Baseline_Model/Create_Baseline_Model.Rmd
analysis on FP

tanish <- fread('data/20K_sample.csv')
# need EMPI for tanish's set, get from EDW data
tanish[rbindlist(list(meds,diagnoses),fill =T),on=.(patient_id = PatientID),EMPI := i.EMPI]
# 0 = no, 1 = neither, 2 = CI
tanish[,Binary_CI := ifelse(prediction == 2,1,0)]
# at least one CI, give 1 for patient level cognitive impairment 
tanish[,patient_CI := ifelse(sum(Binary_CI) > 0,1,0),by=.(patient_id)]
tanish[,num_sequences_patient := .N,by=.(patient_id)]

@@

# view false negatives
View(tanish[patient_id %in% tanish_predictions[patient_CI == 0 & AD_Med_or_ICD_Code == 1,patient_id]])
#view false positives
View(tanish[patient_id %in% tanish_predictions[patient_CI == 1 & AD_Med_or_ICD_Code == 0,patient_id]])

>>>>

tanish <- fread('data/sample_8_12.csv')
# need EMPI for tanish's set, get from EDW data
tanish[rbindlist(list(meds,diagnoses),fill =T),on=.(patient_id = PatientID),EMPI := i.EMPI]
# 0 = no, 1 = neither, 2 = CI
tanish[,Binary_CI := ifelse(predictions == 2,1,0)]
# at least one CI, give 1 for patient level cognitive impairment 
tanish[,patient_CI := ifelse(sum(Binary_CI) > 0,1,0),by=.(patient_id)]
tanish[,num_sequences_patient := .N,by=.(patient_id)]

@@

# view false negatives
View(tanish[patient_id %in% tanish_predictions[patient_CI == 0 & AD_Med_or_ICD_Code == 1,patient_id]])
#view false positives
View(tanish[patient_id %in% tanish_predictions[patient_CI == 1 & AD_Med_or_ICD_Code == 0,patient_id]])
fwrite(tanish[patient_id %in% tanish_predictions[patient_CI == 1 & AD_Med_or_ICD_Code == 0,patient_id]][order(patient_id,-predictions)],file='data/false_positive_sequences.csv')

##### TANISH - ACCURACY MAXIMIZING THRESHOLD #####

library(ROCR)
library(data.table)

# put your test set with binary probs here, 1 col named 'probability' and one named 'annotator_label'
tanish_test_set <- fread("data/test_binary_classification.csv")
# tanish_test_set[,annotator_label := ifelse(annotator_label == 2,1,0)]
# tanish_test_set[annotator_label == 0,probability := 1 - probability]

acc <- performance(prediction(tanish_test_set$probability,tanish_test_set$annotator_label),measure = 'acc')
acc <- data.table(cutoffs = acc@x.values[[1]],accuracy = acc@y.values[[1]])
threshold <- acc[acc[,.I[which.max(accuracy)]],cutoffs]

# .729 sens
sens <- performance(prediction(tanish_test_set$probability,tanish_test_set$annotator_label),measure = 'sens')
sens <- data.table(cutoffs = sens@x.values[[1]],sens = sens@y.values[[1]])
sens[cutoffs == threshold]

# 0.9346939	
spec <- performance(prediction(tanish_test_set$probability,tanish_test_set$annotator_label),measure = 'spec')
spec <- data.table(cutoffs = spec@x.values[[1]],spec= spec@y.values[[1]])
spec[cutoffs == threshold]

# 0.9343537
auc <- performance(prediction(tanish_test_set$probability,tanish_test_set$annotator_label),measure = 'auc')
